---
title: "Academic Article Organizer and Analyzer"
author: "Your Name"
date: "date"
output: html_document
---

```{r setup, include=FALSE}
# Clearing the workspace and setting global chunk options
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load all packages}
# Loading necessary libraries
library(RPostgreSQL)
library(dplyr)
library(dbplyr)
library(data.table)
library(lubridate)
library(reshape2)
library(stringr)
library(tidyverse)
library(readxl)
library(knitr)
library(ggplot2)
library(udpipe)
```

```{r Get a list of existing articles in PDF format}
# Define the base path for articles
base_path <- "path/to/your/articles/directory"

# Listing PDF files in a specific directory
file_list <- as.data.frame(list.files(file.path(base_path, "Deep Learning-Based Recommendation System Systematic Review and Classification"), 
                                      all.files = TRUE, 
                                      full.names = FALSE))
colnames(file_list) <- c("article_title")

# Listing PDF files in the article classification directory
article_list <- as.data.frame(list.files(file.path(base_path, "Article Classification"), 
                                         pattern = ".pdf$", 
                                         full.names = TRUE, 
                                         recursive = TRUE, 
                                         include.dirs = TRUE))

# Getting a list of reviewed articles
old_names <- as.data.frame(list.files(file.path(base_path, "Reviewed Articles/Thesis"), 
                                      all.files = TRUE, 
                                      full.names = FALSE))
colnames(old_names) <- c("article_title")

# Cleaning the file names and removing unwanted characters
old_names <- old_names %>% 
  filter(!article_title %in% c(".", "..", ".DS_Store"))

new_names <- old_names
new_names$article_title <- gsub("[[:punct:]]", " ", new_names$article_title)
new_names$article_title <- gsub("[[:digit:]]+", " ", new_names$article_title)
new_names$article_title <- lapply(new_names$article_title, tolower)
new_names$article_title <- trimws(new_names$article_title)
new_names$article_title <- gsub("\\s+", " ", new_names$article_title)
new_names$article_title <- gsub(" +"," ",new_names$article_title) 
new_names$article_title<- str_to_title(new_names$article_title)
new_names$article_title <- gsub("E Commerce","eCommerce",new_names$article_title) 
new_names$article_title <- gsub(" Pdf","",new_names$article_title) 
new_names <- new_names
new_names <- paste0(new_names$article_title, '.pdf')

# Renaming the files in the specified directory
old.names <- (old_names$article_title)
thesis_path <- file.path(base_path, "Reviewed Articles/Thesis")
file.rename(from = paste0(thesis_path, old.names), to = paste0(thesis_path, new_names))
```

```{r Rename the pre-processing files}
# Renaming files in the pre-processing directory
preprocess_path <- file.path(base_path, "pre-processing/round 2")

old_names <- as.data.frame(list.files(preprocess_path, full.names = FALSE))
colnames(old_names) <- c("article_title")

# Cleaning and modifying file names
new_names <- old_names
new_names$article_title  <- gsub("_.*","",new_names$article_title)
new_names$article_title <- gsub("[[:punct:]]", " ", new_names$article_title)
new_names$article_title <- gsub("[[:digit:]]+", " ", new_names$article_title)
new_names$article_title <- lapply(new_names$article_title, tolower)
new_names$article_title <- trimws(new_names$article_title)
new_names$article_title <- gsub("\\s+", " ", new_names$article_title)
new_names$article_title <- gsub(" +"," ",new_names$article_title) 
new_names$article_title <- gsub(" pdf", "", new_names$article_title)
new_names$article_title<- str_to_sentence(new_names$article_title)
new_names$article_title <- gsub("e commerce|ecommerce","e-commerce",new_names$article_title) 
new_names$article_title <- gsub("E commerce|Ecommerce","E-commerce",new_names$article_title) 
new_names <- new_names
new_names <- paste0(new_names$article_title, '.pdf')
old.names <- (old_names$article_title)

# Renaming files
file.rename(from = paste0(preprocess_path, old.names), to = paste0(preprocess
